---
title: "User Guide"
output: pagedown::html_paged
---

## Using EasyTPRS


This package is designed to make created Thin Plate Regression Splines easy. We essentially provide a wrapper for 'mgcv' and 'spectralGP' to help with creating and visualizing TPRS. TPRS are a method of controlling for unmeasures spatial confounding. You essentially add however many basis splines you want to a spatial regression, and they hopefully absorb some unseen confounding, isolating the true effect. 

Here is an example of a using TPRS in regression: You can see they can be used to correct for confounding and bring the beta estimate for x closer to the truth

```{r, warning=F}
library(EasyTPRS.561final)
set.seed(20)
size = 128
gp=EasyTPRS.561final::simulate_gp(size, .5, plot = F)
confounder=EasyTPRS.561final::simulate_gp(size, .5, plot = F)

x = gp$process + .4*confounder$process
y = x + rnorm(size**2, mean = 0, sd = 1) +  .4*confounder$process
lm(y~x)
```
**As you can see, the true b1 is 1, but the confounder gives us an overestimate.**\ n

```{r}
tprs_obj = EasyTPRS.561final::create_n_2D_TPRS(size, n = 20)
basis_splines = data.matrix(tprs_obj$TPRS)
summary(lm(y~x + basis_splines))
```
**You can see the estimate gets better (closer to one).** \n


####  You can also visualize the splines with visualize_2D_TPRS().

```{r}
visualize_2D_TPRS(tprs_obj = tprs_obj)
```




#### Also as a bonus, you can create a Gaussian process with simulate_gp, a wrapper for the spectralGP package:

```{r}
simulate_gp(128, spectral_density = .5, plot = T)
```

